Mossy Pond mrmr model 1

### 2024-11-13 code/R/VaryingDetection_mrmr.Rmd
initial commit

**Write custom version of mrmr::fit_model()**

Change only line 53. Tell function to pull from my TVD_twostate.stan file

@@

# set paths for Trapdoor captures and surveys
captures <- read.csv("data/54188_capture.csv")  
surveys <- read.csv("data/54188_survey.csv")

data_TVD_model <- mrmr::clean_data(captures, surveys)
```

# Fit the model using the custom function
fit_result <- fit_model_custom(data_TVD_model,
                                chains = 3, 
                                iter_sampling = 1000, 
                                iter_warmup = 400)

modTVD_summary <- fit_result$m_fit$summary()
View(modTVD_summary)

write.csv(modTVD_summary, "Trapdoor_custom_summary")

@@

**Now, run the classic mrmr model on the Trapdoor data to compare with my version**

# Fit the model using the custom function
Trapdoor1_mrmr <- mrmr::fit_model(data_TVD_model,
                                chains = 3, 
                                iter_sampling = 1000, 
                                iter_warmup = 400)

Trapdoor1_summary <- Trapdoor1_mrmr$m_fit$summary()
View(Trapdoor1_summary)

write.csv(Traodoor1_summary, "Trapdoor1_mrmr_summary.csv")

Trapdoor1_summary <- read.csv("Trapdoor1_mrmr_summary.csv")
View(trapdoor_summary)

>>>>

Write custom version of mrmr::fit_model()

@@

# set paths for Trapdoor captures and surveys
captures <- "path/to/capture-example.csv"  
surveys <- "path/to/survey-example.csv"

data_TVD_model <- mrmr::clean_data(captures, surveys)

# Fit the model using the custom function
fit_result <- fit_model_custom(data)

@@

### 2024-11-13 code/R/mrmr_mod1_mossy.Rmd
initial commit

---
title: "Mossy_mrmr_model"
output: html_document
date: "2024-09-12"
---

@@

@@

Run the clean_data function and fit the model

@@

# run the clean_data function
mrmr_mossy_mod1_data <- clean_data(captures, surveys, removals = removals)

@@

>>>>

---
title: "Mossy Pond mrmr model 1"
output: GitHub_document
date: "`r Sys.Date()`"
author: "Your Name"
---

@@

# ATTEMPT TO FIGURE THE PROBLEM OUT
# Include only a subset of columns from captures. This seems to have worked in the past. 
### captures <- unique(captures[ , c(2,3,5,7)])
  # when I create this subset, 5 observations disappear
  # This subset didn't work. Lets try getting rid of CA lake id column
captures <- unique(captures[ , c(3,5,7)])
  # another 2 observations disappeared
# I have not yet run this model

@@

Run the clean_data function

@@

# run the clean_data function
mrmr_mossy_mod1_data <- clean_data(captures, surveys)

fit the model

@@

plot_model(mrmr_mossy_mod1, "abundance")
